(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-10 ms.tex
tdm

\subsection{Stellar Models}
To convert the observed photometric data into physical properties for each
star, we used the publicly available \texttt{isochrones} Python module\footnote{
\url{http://github.com/timothydmorton/isochrones}}, a general-purpose
interpolation tool for stellar model grids.  
This software does trilinear interpolation in mass-age-\feh\ space for any
given set of model grids, thus being able to predict the value for any
physical or photometric property provided by the models at any values of
mass, age, and \feh\ within the boundaries of the grid.

>>>>

\subsection{Stellar Models}
To convert the observed photometric data into physical properties for each
star, we used the publicly available \texttt{isochrones} Python module\footnote{
\url{http://github.com/timothydmorton/isochrones}}, a general-purpose
interpolation tool for stellar model grids.  
This software does trilinear interpolation in mass--age--\feh\ space for any
given set of model grids, thus being able to predict the value for any
physical or photometric property provided by the models at any values of
mass, age, and \feh\ within the boundaries of the grid.
